---
title: "Gravid Trap Analyses"
author: "Elisabeth Nelson"
date: "2023-02-05"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(readr)
pacman::p_load(
  lubridate,  # general package for handling and converting dates  
  linelist,   # has function to "guess" messy dates
  aweek,      # another option for converting dates to weeks, and weeks to dates
  zoo,        # additional date/time functions
  tidyverse,  # data management and visualization  
  rio, #importing data
  here, #relative file pathways
  janitor, #data cleaning and tables
  epikit) #ag_categories function
library(ggplot2)
library(stats); library(splines); library(gam); library(dlnm)
library(scales)
library(patchwork)
library(survival)
library(plotly)
library(survminer)

```

## Only Gravid Traps
```{r}

core_traps_ff_gravid <- core_traps_ff %>%
  filter(Trap.Type == "Gravid Trap") %>% 
  filter(Date > '2006-01-01')

```

## Species Density vs. Climate
See bottom for more accurate plots
```{r}

species_table_g <- core_traps_ff_gravid %>%
  dplyr::select(Species, Date, X..Mosquitoes) %>%
  rename("species" = Species, 
         "date" = Date, 
         "num_caught" =  X..Mosquitoes)

species_by_year_g <- species_table_g %>%
  group_by(species) %>%
  summarize(num_caught = sum(num_caught))

species_by_year_g %>%
ggplot(aes(x = species, y = num_caught))+
  geom_bar(stat = "identity")+
  geom_jitter(width = 0.15)+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))+
  xlab("Species")+
  ylab("Mosquitoes Caught")+
  labs(title = "Gravid Traps since 2006")
  

```

## First WNV Positive and Predictors 
```{r}
# create a new column of days since June 1st for 1st WNV+, do for overall, cx pipiens, and cx restuans
core_traps_ff_WNV_g <- core_traps_ff_gravid %>%
  mutate(WNV_pos = case_when(Virus == "WNV" ~ 1,
                             Virus == "WNV, HJ" ~ 1, 
                             Virus == "WNV & HJ" ~ 1,
                             Virus == "EEE & WNV" ~ 1,
                             Virus != "WNV" ~ 0)) %>% 
  filter(WNV_pos == 1)

core_traps_ff_WNV_g <- core_traps_ff_WNV_g %>%
  arrange(Site, Species, Date) %>%
  mutate(year = year(Date)) %>%
  group_by(Site,Species, year) %>%
  mutate(june_1 = "June-01") %>%
  unite("june1", year:june_1, remove = F) %>%
  mutate(june1 = as.Date(june1, "%Y_%b-%d"),
         sampleN=row_number(),
        days_since_june_1 = as.numeric(Date - june1))

core_traps_ff_WNV_first_g <- core_traps_ff_WNV_g %>%
  arrange(Site,Species, year) %>%
  group_by(Site,Species, year) %>%
  filter(row_number() == 1) %>%
  filter(Species == "culex pipiens" | Species == "culex restuans")

################ Map ################
core_traps_ff_WNV_map_g <- core_traps_ff_WNV_first_g %>%
  mutate(Site = as.character(Site)) %>%
  group_by(Site) %>%
  summarize(avg_days = mean(days_since_june_1), 
            latitude = latitude, 
            longitude = longitude)

ggplot()+
  geom_polygon(data=CT_2, aes(x=long, y=lat, group=group), fill=NA, colour='black', alpha=0)+
  geom_point(data = core_traps_ff_WNV_map_g, aes(x = longitude, y = latitude, col = avg_days), size = 4)+
  scale_color_distiller(name = "Average Days Since June 1st", 
                       palette = "Blues", 
                       direction = 1)+
   theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "white", color = NA))


######### Smooth plots ###########

# First positives smooth cx. pipiens and resutans combined 
core_traps_ff_WNV_first_g %>%
  ungroup() %>%
  group_by(year) %>%
  summarize(avg_days = mean(days_since_june_1), 
            latitude = latitude, 
            longitude = longitude) %>%
  ggplot(aes(x = year, y = avg_days))+
    geom_line()+
    geom_point()+
    geom_smooth()+
    theme_classic()+
    labs(x = "Year", y = "Days Since June 1", title = "Average Days Since June 1")

# First positives smooth by species
core_traps_ff_WNV_first_g %>%
  ungroup() %>%
  group_by(year) %>%
  summarize(avg_days = mean(days_since_june_1), 
            latitude = latitude, 
            longitude = longitude, 
            Species = Species) %>%
  ggplot(aes(year, avg_days, col = Species), na.rm = T)+
  geom_line()+
  geom_smooth()+
  facet_wrap(~Species)+
  theme_classic()+
  labs(x = "Year", y = "Days Since June 1", title = "Average Days Since June 1")
```


```{r}
##########################################
############ Survival Model ##############
##########################################

######################## basic survival model ################################
  
core_traps_ff_surv_g <- core_traps_ff_gravid %>%
  mutate(WNV_pos = case_when(Virus == "WNV" ~ 1,
                             Virus == "WNV, HJ" ~ 1, 
                             Virus == "WNV & HJ" ~ 1,
                             Virus == "EEE & WNV" ~ 1,
                             Virus != "WNV" ~ 0))

# add yearly trap type total by species
core_traps_ff_surv_g <- core_traps_ff_surv_g %>%
  group_by(land_class, Species, year(Date)) %>%
  mutate(yearly_trap_type_tot = sum(X..Mosquitoes))

# trap type totals
trap_type_totals_g <- core_traps_ff_gravid %>%
  ungroup() %>%
  distinct(Site, .keep_all = T)
tot_city <- sum(trap_type_totals_g$land_class == "city")
tot_suburb <- sum(trap_type_totals_g$land_class == "suburb")
tot_town <- sum(trap_type_totals_g$land_class == "town")
tot_rural <- sum(trap_type_totals_g$land_class == "rural")

# if WNV = 1, then days since june 1st, if WNV = 0, days since june first = days since last trapping
core_traps_ff_surv_1_g <- core_traps_ff_surv_g %>%
  arrange(Site, Species, Date) %>%
  mutate(year = year(Date)) %>%
  group_by(Site,Species, year) %>%
  mutate(last_trap = max(Date)) %>% 
  mutate(june_1 = "June-01", .before = last_trap) %>%
  unite("june1", year:june_1, remove = F) %>%
  mutate(june1 = as.Date(june1, "%Y_%b-%d"), 
         sampleN=row_number(),
         days_since_june_1 = if_else(WNV_pos == 1, 
                as.numeric(Date - june1), 
                as.numeric(last_trap - june1)))

# Get only one neg obs per year per species per trap
core_traps_ff_surv_2_g <- core_traps_ff_surv_1_g %>%
  arrange(Site, Species, Date) %>%
  group_by(Site,Species, year) %>%
  dplyr::slice(which.min(days_since_june_1)) 
 # dplyr::filter(if_else(WNV_pos == 1, 
  #                      min(days_since_june_1), 
   #                     mean(days_since_june_1)))
  
core_traps_ff_surv_2_g <- core_traps_ff_surv_2_g %>%
  arrange(Site,Species, year) %>%
  group_by(Site,Species, year) %>%
  mutate(land_class = as.factor(land_class))

# construct model
survobj_g <- Surv(time = core_traps_ff_surv_2_g$days_since_june_1, 
                    event = core_traps_ff_surv_2_g$WNV_pos)

surv_fit_g <- survfit(survobj_g ~ 1)
summary(surv_fit_g)
print(surv_fit_g, print.rmean = F)
  # rmean refers to the area under the curve (estricted mean survival time) which is mainly used in cancer research


########### for pipiens ###########
cxp_surv_g <- core_traps_ff_surv_2_g %>%
  dplyr::filter(Species == "culex pipiens") %>%
  group_by(Site, Date) %>%
  mutate(days_over_trap_total = (days_since_june_1/yearly_trap_type_tot)*100, 
         days_x_trap_type = days_since_june_1*yearly_trap_type_tot) %>%
  ungroup()

survobj_cxp_g <- Surv(time = cxp_surv_g$days_since_june_1, 
                    event = cxp_surv_g$WNV_pos)

surv_fit_cxp_g <- survfit(survobj_cxp_g ~ 1)
summary(surv_fit_cxp_g)
print(surv_fit_cxp_g, print.rmean = F)
str(surv_fit_cxp_g)

plot(surv_fit_cxp_g, 
     xlab = "Days Since June 1", 
     ylab = "Probability of Not Isolating WNV", 
     main = "Culex Pipiens First WNV Positive Survival Curve")

# add event marks, cumulative hazard, and legend
plot(surv_fit_cxp_g,
  xlab = "Days Since June 1", 
  ylab = "Probability of Not Isolating WNV",       
  mark.time = TRUE,              # mark events on the curve: a "+" is printed at every event
  conf.int = FALSE,              # do not plot the confidence interval
  main = "Culex Pipiens First WNV Positive Survival Curve")
lines(surv_fit_cxp_g,
  lty = 3,             # use different line type for clarity
  fun = "event",       # draw the cumulative events instead of the survival 
  mark.time = FALSE,
  conf.int = FALSE)
legend( "topright",                         # position of legend
  legend = c("Survival", "Cum. Mortality"), # legend text 
  lty = c(1, 3),                            # line types to use in the legend
  cex = .85,                                # parametes that defines size of legend text
  bty = "n"                                 # no box type to be drawn for the legend
  )

########## for restuans #########
cxr_surv_g <- core_traps_ff_surv_2_g %>%
  dplyr::filter(Species == "culex restuans") %>%
  group_by(Site, Date) %>%
  mutate(days_over_trap_total = (days_since_june_1/yearly_trap_type_tot)*100, 
         days_x_trap_type = days_since_june_1*yearly_trap_type_tot) %>%
  ungroup()

survobj_cxr_g <- Surv(time = cxr_surv_g$days_since_june_1, 
                    event = cxr_surv_g$WNV_pos)

surv_fit_cxr_g <- survfit(survobj_cxr_g ~ 1)
summary(surv_fit_cxr_g)
print(surv_fit_cxr_g, print.rmean = F)

plot(surv_fit_cxr_g, 
     xlab = "Days Since June 1", 
     ylab = "Probability of Not Isolating WNV", 
     main = "Culex Restuans First WNV Positive Survival Curve")

# add event marks, cumulative hazard, and legend
plot(surv_fit_cxr_g,
  xlab = "Days Since June 1", 
  ylab = "Probability of Not Isolating WNV",       
  mark.time = TRUE,              # mark events on the curve: a "+" is printed at every event
  conf.int = FALSE,              # do not plot the confidence interval
  main = "Culex Restuans First WNV Positive Survival Curve")
lines(surv_fit_cxr_g,
  lty = 3,             # use different line type for clarity
  fun = "event",       # draw the cumulative events instead of the survival 
  mark.time = FALSE,
  conf.int = FALSE)
legend( "topright",                         # position of legend
  legend = c("Survival", "Cum. Mortality"), # legend text 
  lty = c(1, 3),                            # line types to use in the legend
  cex = .85,                                # parametes that defines size of legend text
  bty = "n"                                 # no box type to be drawn for the legend 
  )

########################### log rank test ############################

######### for species  ###########
surv_fit_species_g <- survfit(Surv(days_since_june_1, WNV_pos) ~ Species, data = core_traps_ff_surv_2_g)

# set colors
col_species <- viridis::viridis(n = 47, alpha = 1, begin = 0, end = 1, option = "viridis")

# create plot
plot(
  surv_fit_species_g,
  col = col_species,
  xlab = "Days Since June 1", 
  ylab = "Probability of Not Isolating WNV")

# add legend
legend(
  "bottomleft",
  legend = c(unique(core_traps_ff_surv_2_g$Species)),
  col = col_species,
  lty = 1,
  cex = .3,
  bty = "n", 
  ncol = 5)

# calculate the difference between the survival curves
survdiff(Surv(days_since_june_1, WNV_pos) ~ Species, data = core_traps_ff_surv_2_g)

######### for culex pipiens and culex restuans ############
cx_surv_g <- core_traps_ff_surv_2_g %>%
  filter(Species == "culex pipiens" | Species == "culex restuans") %>%
  droplevels()

cx_surv_g <- cx_surv_g %>%
  group_by(Site, Species, Date) %>%
  mutate(days_over_trap_total = (days_since_june_1/yearly_trap_type_tot)*100, 
         days_x_trap_type = days_since_june_1*yearly_trap_type_tot) %>%
  ungroup()
  
surv_fit_cx_g <- survfit(Surv(days_over_trap_total, WNV_pos) ~ Species, data = cx_surv_g)

# set colors
col_species_2 <- viridis::viridis(n = 4, alpha = 1, begin = 0, end = 1, option = "viridis")

# create plot
plot(
  surv_fit_cx_g,
  col = col_species_2,
  xlab = "Days Since June 1", 
  ylab = "Probability of Not Isolating WNV")

# add legend
legend(
  "bottomleft",
  legend = c(unique(cx_surv$Species)),
  col = col_species_2,
  lty = 1,
  cex = .9,
  bty = "n")

# calculate the difference between the survival curves
survdiff(Surv(days_since_june_1, WNV_pos) ~ Species, data = cx_surv_g)

# other plotting method
survminer::ggsurvplot(
    surv_fit_cx_g, 
    data = cx_surv_g,          # again specify the data used to fit  
    conf.int = T,              # do not show confidence interval of KM estimates
    surv.scale = "percent",        # present probabilities in the y axis in %
    break.time.by = 20,            # present the time axis with an increment of 10 days
    xlab = "Days Since June 1", 
    ylab = "Probability of Not Isolating WNV",
    pval = T,                      # print p-value of Log-rank test 
    #pval.coord = c(40,.91),        # print p-value at these plot coordinates
    risk.table = T,                # print the risk table at bottom 
    legend.title = "Species",       # legend characteristics
    legend.labs = c(unique(cx_surv_g$Species)),
    font.legend = 10, 
    palette = "Dark2",             # specify color palette 
    surv.median.line = "hv",       # draw horizontal and vertical lines to the median survivals
    ggtheme = theme_light()        # simplify plot background
)


######### for different land cover  ##########
surv_fit_land_g <- survfit(Surv(days_since_june_1, WNV_pos) ~ land_class, data = core_traps_ff_surv_2_g)

# set colors
col_land <- viridis::viridis(n = 5, alpha = 1, begin = 0, end = 1, option = "viridis")

# create plot
plot(
  surv_fit_land_g,
  col = col_land,
  xlab = "Days Since June 1", 
  ylab = "Probability of Not Isolating WNV")

# add legend
legend(
  "bottomleft",
  legend = c(unique(core_traps_ff_surv_2_g$land_class)),
  col = col_land,
  lty = 1,
  cex = .9,
  bty = "n")

# calculate the difference between the survival curves
survdiff(Surv(days_since_june_1, WNV_pos) ~ land_class, data = core_traps_ff_surv_2_g)



######### for different land cover between cx. pipiens and cx. restuans #######
surv_fit_land_cx_g <- survfit(Surv(days_since_june_1, WNV_pos) ~ land_class, data = cx_surv_g)
surv_fit_land_cx_scaled_g <- survfit(Surv(days_over_trap_total, WNV_pos) ~ land_class, data = cx_surv_g)

# set colors
col_land <- viridis::viridis(n = 5, alpha = 1, begin = 0, end = 1, option = "viridis")

# create plot
plot(
  surv_fit_land_cx_g,
  col = col_land,
  xlab = "Days Since June 1", 
  ylab = "Probability of Not Isolating WNV")

# add legend
legend(
  "bottomleft",
  legend = c(unique(core_traps_ff_surv_2_g$land_class)),
  col = col_land,
  lty = 1,
  cex = .9,
  bty = "n")

# calculate the difference between the survival curves
survdiff(Surv(days_since_june_1, WNV_pos) ~ land_class, data = cx_surv_g)

# other plotting method
survminer::ggsurvplot(
    surv_fit_land_cx_g, 
    data = cx_surv_g,          # again specify the data used to fit  
    conf.int = T,              # do not show confidence interval of KM estimates
    surv.scale = "percent",        # present probabilities in the y axis in %
    break.time.by = 20,            # present the time axis with an increment of 10 days
    xlab = "Days Since June 1", 
    ylab = "Probability of Not Isolating WNV",
    pval = T,                      # print p-value of Log-rank test 
    #pval.coord = c(40,.91),        # print p-value at these plot coordinates
    risk.table = T,                # print the risk table at bottom 
    legend.title = "Land Cover",       # legend characteristics
    legend.labs = c(unique(core_traps_ff_surv_2_g$land_class)),
    font.legend = 10, 
    palette = "Dark2",             # specify color palette 
    surv.median.line = "hv",       # draw horizontal and vertical lines to the median survivals
    ggtheme = theme_light()        # simplify plot background
)

# scaled
survminer::ggsurvplot(
    surv_fit_land_cx_scaled_g, 
    data = cx_surv_g,          # again specify the data used to fit  
    conf.int = T,              # do not show confidence interval of KM estimates
    surv.scale = "percent",        # present probabilities in the y axis in %
    break.time.by = 20,            # present the time axis with an increment of 10 days
    xlab = "Days Since June 1/Trap Type Yearly Total x 100 (by species)", 
    ylab = "Probability of Not Isolating WNV",
    pval = T,                      # print p-value of Log-rank test 
    #pval.coord = c(40,.91),        # print p-value at these plot coordinates
    risk.table = T,                # print the risk table at bottom 
    legend.title = "Land Cover",       # legend characteristics
    legend.labs = c(unique(core_traps_ff_surv_2_g$land_class)),
    font.legend = 10, 
    palette = "Dark2",             # specify color palette 
    surv.median.line = "hv",       # draw horizontal and vertical lines to the median survivals
    ggtheme = theme_light()        # simplify plot background
)

####### for just cx. pipiens ########
surv_fit_land_cxp_g <- survfit(Surv(days_since_june_1, WNV_pos) ~ land_class, data = cxp_surv_g)

# set colors
col_land <- viridis::viridis(n = 5, alpha = 1, begin = 0, end = 1, option = "viridis")

# create plot
plot(
  surv_fit_land_cxp_g,
  col = col_land,
  xlab = "Days Since June 1", 
  ylab = "Probability of Not Isolating WNV")

# add legend
legend(
  "bottomleft",
  legend = c(unique(core_traps_ff_surv_2_g$land_class)),
  col = col_land,
  lty = 1,
  cex = .9,
  bty = "n")

# calculate the difference between the survival curves
survdiff(Surv(days_since_june_1, WNV_pos) ~ land_class, data = cxp_surv_g)

survminer::ggsurvplot(
    surv_fit_land_cxp_g, 
    data = cxp_surv_g,          # again specify the data used to fit  
    conf.int = T,              # do not show confidence interval of KM estimates
    surv.scale = "percent",        # present probabilities in the y axis in %
    break.time.by = 20,            # present the time axis with an increment of 10 days
    xlab = "Days Since June 1", 
    ylab = "Probability of Not Isolating WNV",
    pval = T,                      # print p-value of Log-rank test 
    #pval.coord = c(40,.91),        # print p-value at these plot coordinates
    risk.table = T,                # print the risk table at bottom 
    legend.title = "Land Cover",       # legend characteristics
    legend.labs = c(unique(core_traps_ff_surv_2_g$land_class)),
    font.legend = 10, 
    palette = "Dark2",             # specify color palette 
    surv.median.line = "hv",       # draw horizontal and vertical lines to the median survivals
    ggtheme = theme_light()        # simplify plot background
)

#### scaled
surv_fit_land_cxp_scaled_g  <- survfit(Surv(days_over_trap_total, WNV_pos) ~ land_class, data = cxp_surv_g)

# other plotting method
survminer::ggsurvplot(
    surv_fit_land_cxp_scaled_g, 
    data = cxp_surv_g,          # again specify the data used to fit  
    conf.int = T,              # do not show confidence interval of KM estimates
    surv.scale = "percent",        # present probabilities in the y axis in %
    break.time.by = 20,            # present the time axis with an increment of 10 days
    xlab = "Days Since June 1/Trap Type Yearly Total x 100", 
    ylab = "Probability of Not Isolating WNV",
    pval = T,                      # print p-value of Log-rank test 
    #pval.coord = c(40,.91),        # print p-value at these plot coordinates
    risk.table = T,                # print the risk table at bottom 
    legend.title = "Land Cover",       # legend characteristics
    legend.labs = c(unique(core_traps_ff_surv_2_g$land_class)),
    font.legend = 10, 
    palette = "Dark2",             # specify color palette 
    surv.median.line = "hv",       # draw horizontal and vertical lines to the median survivals
    ggtheme = theme_light()        # simplify plot background
)

########## for just cx. restuans ##############
surv_fit_land_cxr_g <- survfit(Surv(days_since_june_1, WNV_pos) ~ land_class, data = cxr_surv_g)

# set colors
col_land <- viridis::viridis(n = 5, alpha = 1, begin = 0, end = 1, option = "viridis")

# create plot
plot(
  surv_fit_land_cxr_g,
  col = col_land,
  xlab = "Days Since June 1", 
  ylab = "Probability of Not Isolating WNV")

# add legend
legend(
  "bottomleft",
  legend = c(unique(core_traps_ff_surv_2_g$land_class)),
  col = col_land,
  lty = 1,
  cex = .9,
  bty = "n")

# calculate the difference between the survival curves
survdiff(Surv(days_since_june_1, WNV_pos) ~ land_class, data = cxr_surv_g)

# other plotting method
survminer::ggsurvplot(
    surv_fit_land_cxp_g, 
    data = cxp_surv_g,          # again specify the data used to fit  
    conf.int = T,              # do not show confidence interval of KM estimates
    surv.scale = "percent",        # present probabilities in the y axis in %
    break.time.by = 20,            # present the time axis with an increment of 10 days
    xlab = "Days Since June 1", 
    ylab = "Probability of Not Isolating WNV",
    pval = T,                      # print p-value of Log-rank test 
    #pval.coord = c(40,.91),        # print p-value at these plot coordinates
    risk.table = T,                # print the risk table at bottom 
    legend.title = "Land Cover",       # legend characteristics
    legend.labs = c(unique(core_traps_ff_surv_2$land_class)),
    font.legend = 10, 
    palette = "Dark2",             # specify color palette 
    surv.median.line = "hv",       # draw horizontal and vertical lines to the median survivals
    ggtheme = theme_light()        # simplify plot background
)

#### scaled
surv_fit_land_cxr_scaled_g  <- survfit(Surv(days_over_trap_total, WNV_pos) ~ land_class, data = cxr_surv_g)

# other plotting method
survminer::ggsurvplot(
    surv_fit_land_cxr_scaled_g, 
    data = cxr_surv_g,          # again specify the data used to fit  
    conf.int = T,              # do not show confidence interval of KM estimates
    surv.scale = "percent",        # present probabilities in the y axis in %
    break.time.by = 20,            # present the time axis with an increment of 10 days
    xlab = "Days Since June 1/Trap Type Yearly Total x 100", 
    ylab = "Probability of Not Isolating WNV",
    pval = T,                      # print p-value of Log-rank test 
    #pval.coord = c(40,.91),        # print p-value at these plot coordinates
    risk.table = T,                # print the risk table at bottom 
    legend.title = "Land Cover",       # legend characteristics
    legend.labs = c(unique(core_traps_ff_surv_2_g$land_class)),
    font.legend = 10, 
    palette = "Dark2",             # specify color palette 
    surv.median.line = "hv",       # draw horizontal and vertical lines to the median survivals
    ggtheme = theme_light()        # simplify plot background
)
```


Urban and Culex Pipiens show significantly greater probability of WNV positivity. Pipiens and Restuans both show Urban > Suburban > Rural, but Pipiens showed an 80% probability in urban areas. 

Hazard ratios in the best fit model: culex restuans = 0.9076 (based on cx. pipiens), rural = 0.4170 (based on suburban), urban = 1.5747 (based on suburban), tmean = 1.0716, lag_2_tmean = 1.0883, lag_4_tmean = 1.0640, lag_6_tmean = 1.0503, lag_8_tmean = 1.0278, ppt = 1.3695



```{r}
# summarize trap types 
cx_surv_summary_g <- cx_surv_g %>%
  distinct(land_class, year(Date), .keep_all = T) %>%
  mutate(yearly_tot_by_type = 0,
         yearly_tot_by_type = if_else(land_class == "city", yearly_trap_type_tot/tot_city, yearly_tot_by_type), 
         yearly_tot_by_type = if_else(land_class == "suburb", yearly_trap_type_tot/tot_suburb, yearly_tot_by_type),
         yearly_tot_by_type = if_else(land_class == "town", yearly_trap_type_tot/tot_town, yearly_tot_by_type),
         yearly_tot_by_type = if_else(land_class == "rural", yearly_trap_type_tot/tot_rural, yearly_tot_by_type))

ggplot(aes(Date, yearly_tot_by_type, color = land_class), data = cx_surv_summary_g)+
  geom_line()+
  xlab("Year")+
  ylab("Total Cx. pipiens & Cx. restuans caught/Total Trap Type")+
  labs(color = "Trap Land Cover")+
  theme_classic()

# cx. pipiens 
cxp_surv_summary_g <- cxp_surv_g %>%
  distinct(land_class, year(Date), .keep_all = T) %>%
  mutate(yearly_tot_by_type = 0,
         yearly_tot_by_type = if_else(land_class == "city", yearly_trap_type_tot/tot_city, yearly_tot_by_type), 
         yearly_tot_by_type = if_else(land_class == "suburb", yearly_trap_type_tot/tot_suburb, yearly_tot_by_type),
         yearly_tot_by_type = if_else(land_class == "town", yearly_trap_type_tot/tot_town, yearly_tot_by_type),
         yearly_tot_by_type = if_else(land_class == "rural", yearly_trap_type_tot/tot_rural, yearly_tot_by_type))

ggplot(aes(Date, yearly_tot_by_type, color = land_class), data = cxp_surv_summary_g)+
  geom_line()+
  xlab("Year")+
  ylab("Total Cx. pipiens caught/Total Trap Type")+
  labs(color = "Trap Land Cover")+
  theme_classic()

# cx. restuans
cxr_surv_summary_g <- cxr_surv_g %>%
  distinct(land_class, year(Date), .keep_all = T) %>%
  mutate(yearly_tot_by_type = 0,
         yearly_tot_by_type = if_else(land_class == "city", yearly_trap_type_tot/tot_city, yearly_tot_by_type), 
         yearly_tot_by_type = if_else(land_class == "suburb", yearly_trap_type_tot/tot_suburb, yearly_tot_by_type),
         yearly_tot_by_type = if_else(land_class == "town", yearly_trap_type_tot/tot_town, yearly_tot_by_type),
         yearly_tot_by_type = if_else(land_class == "rural", yearly_trap_type_tot/tot_rural, yearly_tot_by_type))

ggplot(aes(Date, yearly_tot_by_type, color = land_class), data = cxr_surv_summary_g)+
  geom_line()+
  xlab("Year")+
  ylab("Total Cx. restuans caught/Total Trap Type")+
  labs(color = "Trap Land Cover")+
  theme_classic()

```


## Last Positives
```{r}

core_traps_ff_WNV_last_g <- core_traps_ff_WNV_g %>%
  arrange(Site,Species, year) %>%
  group_by(Site,Species, year) %>%
  filter(row_number() == max(row_number())) %>%
  filter(Species == "culex pipiens" | Species == "culex restuans")

################ Map ################
core_traps_ff_WNV_last_map_g <- core_traps_ff_WNV_last_g %>%
  mutate(Site = as.character(Site)) %>%
  group_by(Site) %>%
  summarize(avg_days = mean(days_since_june_1), 
            latitude = latitude, 
            longitude = longitude)

ggplot()+
  geom_polygon(data=CT_2, aes(x=long, y=lat, group=group), fill=NA, colour='black', alpha=0)+
  geom_point(data = core_traps_ff_WNV_last_map_g, aes(x = longitude, y = latitude, col = avg_days), size = 4)+
  scale_color_distiller(name = "Average Days Since June 1st", 
                       palette = "Blues", 
                       direction = 1)+
   theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "white", color = NA))


######### Smooth plots ###########

# First positives smooth cx. pipiens and resutans combined 
core_traps_ff_WNV_last_g %>%
  ungroup() %>%
  group_by(year) %>%
  summarize(avg_days = mean(days_since_june_1), 
            latitude = latitude, 
            longitude = longitude) %>%
  ggplot(aes(x = year, y = avg_days))+
    geom_line()+
    geom_point()+
    geom_smooth()+
    theme_classic()+
    labs(x = "Year", y = "Days Since June 1", title = "Average Days Since June 1")

# First positives smooth by species
core_traps_ff_WNV_last_g %>%
  ungroup() %>%
  group_by(year) %>%
  summarize(avg_days = mean(days_since_june_1), 
            latitude = latitude, 
            longitude = longitude, 
            Species = Species) %>%
  ggplot(aes(year, avg_days, col = Species), na.rm = T)+
  geom_line()+
  geom_smooth()+
  facet_wrap(~Species)+
  theme_classic()+
  labs(x = "Year", y = "Days Since June 1", title = "Average Days Since June 1")

```

## Culex pipiens populations vs. WNV activity
```{r}
# abundance bar plot
culex_pipiens_g <- core_traps_ff_gravid %>%
  filter(Species == "culex pipiens") %>%
  group_by(year(Date)) %>%
  mutate(year_total = sum(X..Mosquitoes))

culex_pipiens_g %>%
ggplot(aes(x = year(Date), y = year_total))+
  geom_bar(stat = "identity")+
  geom_jitter(width = 0.15)+
  theme(axis.text.x = element_text(angle = 90))+
  theme_classic()

# abundance plot
core_traps_ff_gravid %>%
  filter(Species == "culex pipiens") %>%
  group_by(year(Date)) %>%
  mutate(year_total = sum(X..Mosquitoes)) %>%
  ggplot(aes(x = year(Date), y = year_total))+
    geom_line(color = "blue")+
    #facet_wrap(~species, scales = 'free_y')+
    theme_classic()+
  ylab("Culex pipiens Caught")+
  xlab("Year")

  
############# plot over CT map  #############
cxp_map_g <- core_traps_ff_gravid %>%
  filter(Species == "culex pipiens") %>%
  ungroup() %>%
  group_by(Site) %>%
  summarize(site_tot = sum(X..Mosquitoes), 
            latitude = latitude, 
            longitude = longitude)
ggplot()+
  geom_polygon(data=CT_2, aes(x=long, y=lat, group=group), fill=NA, colour='black', alpha=0)+
  geom_point(data = cxp_map_g, aes(x = longitude, y = latitude, group = factor(Site), size = site_tot), col = "blue")+
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "white", color = NA))+
  labs(size = "Total Culex pipiens Caught")

```
Needed to average across traps (so across the state) to just plot climate vs. Cx. pipiens abundance...
Should I do a GAM or GLM????
control for seasonality --> use harmonics (ask GiGi or Kelsey)


## Culex restuans populations vs. WNV activity
```{r}
# abundance bar plot
culex_restuans_g <- core_traps_ff_gravid %>%
  filter(Species == "culex restuans") %>%
  group_by(year(Date)) %>%
  mutate(year_total = sum(X..Mosquitoes))

culex_restuans_g %>%
ggplot(aes(x = year(Date), y = year_total))+
  geom_bar(stat = "identity")+
  geom_jitter(width = 0.15)+
  theme(axis.text.x = element_text(angle = 90))+
  theme_classic()

# abundance plot
core_traps_ff_gravid %>%
  filter(Species == "culex restuans") %>%
  group_by(year(Date)) %>%
  mutate(year_total = sum(X..Mosquitoes)) %>%
  ggplot(aes(x = year(Date), y = year_total))+
    geom_line(color = "blue")+
    #facet_wrap(~species, scales = 'free_y')+
    theme_classic()+
  ylab("Culex restauns Caught")+
  xlab("Year")

############# plot over CT map  #############
cxr_map_g <- core_traps_ff_gravid %>%
  filter(Species == "culex restuans") %>%
  ungroup() %>%
  group_by(Site) %>%
  summarize(site_tot = sum(X..Mosquitoes), 
            latitude = latitude, 
            longitude = longitude)
ggplot()+
  geom_polygon(data=CT_2, aes(x=long, y=lat, group=group), fill=NA, colour='black', alpha=0)+
  geom_point(data = cxr_map_g, aes(x = longitude, y = latitude, group = factor(Site), size = site_tot), col = "navy")+
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "white", color = NA))+
  labs(size = "Total Culex restuans Caught")

```

## Model the two species together (Cx. pipiens + Cx. restuans)
```{r}
# abundance plot
core_traps_ff_gravid %>%
  filter(Species == "culex pipiens" | Species == "culex restuans") %>%
  group_by(year(Date), Species) %>%
  mutate(year_total = sum(X..Mosquitoes)) %>%
  ggplot(aes(x = year(Date), y = year_total, group = Species, color = Species))+
    geom_line()+
    #facet_wrap(~species, scales = 'free_y')+
    theme_classic()+
  ylab("Culex Caught")+
  xlab("Year")

cxp_cxr_table_g <- species_table_g %>%
  mutate(species = as.character(species)) %>%
  filter(species == "culex pipiens" | species == "culex restuans") %>%
  group_by(species, year(date)) %>%
  mutate(year_total = sum(num_caught))

cxp_cxr_table_2_g <- cxp_cxr_table_g %>%
  ungroup() %>%
  group_by(Site, species) %>%
  summarize(species_total = sum(num_caught))%>%
  pivot_wider(names_from = species, 
              values_from = species_total) %>%
  mutate(species_ratio = `culex pipiens`/`culex restuans`)

ggplot(cxp_cxr_table_g, aes(x = year(date), y = year_total, group = species, col = species ))+
  geom_line()+
  #facet_wrap(~species, scales = 'free_y')+
  theme_classic()

cxp_cxr_table_g %>%
  mutate(Site = as.character(Site))

cxp_cxr_climate_g <- left_join(cxp_cxr_table_g, trap_climate, by = c("Site" = "Name", "date" = "Date"))


## MAP of species ratio
cxp_cxr_map_g <- left_join(cxp_cxr_table_2_g, trap_location_land_cover, by = c("Site" = "location")) %>%
  ungroup 

ggplot()+
  geom_polygon(data = CT_2, aes(x=long, y=lat, group=group), fill=NA, colour='black', alpha=0)+
  geom_point(data = cxp_cxr_map_g, aes(x = longitude, y = latitude, group = factor(Site), 
                                     size = species_ratio), color = "royal blue")+
   theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "white", color = NA))+
  labs(size = "Culex pipiens/Culex restuans")

## Map of positivity ratio
WNV_cxp_cxr_table_g <- core_traps_ff_WNV_g %>%
  ungroup() %>%
  filter(Species == "culex pipiens" | Species == "culex restuans") %>%
  group_by(Site, Species) %>%
  summarize(species_total_WNV = sum(WNV_pos))%>%
  pivot_wider(names_from = Species, 
              values_from = species_total_WNV) %>%
  mutate(species_ratio_WNV = `culex pipiens`/`culex restuans`) %>%
  na.omit()

WNV_cxp_cxr_table_g <- WNV_cxp_cxr_table_g %>%
  mutate(species_ratio_WNV = if_else(species_ratio_WNV == Inf, 0, species_ratio_WNV))
  

WNV_cxp_cxr_map_g <- left_join(WNV_cxp_cxr_table_g, trap_location_land_cover, by = c("Site" = "location")) %>%
  ungroup 

ggplot()+
  geom_polygon(data = CT_2, aes(x=long, y=lat, group=group), fill=NA, colour='black', alpha=0)+
  geom_point(data = WNV_cxp_cxr_map_g, aes(x = longitude, y = latitude, group = factor(Site), 
                                     size = species_ratio_WNV), color = "tomato")+
   theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "white", color = NA))+
  labs(size = "Cx pipiens WNV + / Cx restuans WNV +")

```



